% Copyright 2013 Christophe-Marie Duquesne <chmd@chmd.fr>
% Copyright 2014 Mark Szepieniec <http://github.com/mszep>
% 
% ConText style for making a resume with pandoc. Inspired by moderncv.
% 
% This CSS document is delivered to you under the CC BY-SA 3.0 License.
% https://creativecommons.org/licenses/by-sa/3.0/deed.en_US

\startmode[*mkii]
  \enableregime[utf-8]  
  \setupcolors[state=start]
\stopmode

\setupcolor[hex]
\definecolor[titlegrey][h=757575]
\definecolor[sectioncolor][h=397249]
\definecolor[rulecolor][h=9cb770]

% Enable hyperlinks
\setupinteraction[state=start, color=sectioncolor]

\setuppapersize [A4][A4]
\setuplayout    [width=middle, height=middle,
                 backspace=20mm, cutspace=0mm,
                 topspace=10mm, bottomspace=20mm,
                 header=0mm, footer=0mm]

%\setuppagenumbering[location={footer,center}]

\setupbodyfont[11pt, helvetica]

\setupwhitespace[medium]

\setupblackrules[width=31mm, color=rulecolor]

\setuphead[chapter]      [style=\tfd]
\setuphead[section]      [style=\tfd\bf, color=titlegrey, align=middle]
\setuphead[subsection]   [style=\tfb\bf, color=sectioncolor, align=right,
                          before={\leavevmode\blackrule\hspace}]
\setuphead[subsubsection][style=\bf]

\setuphead[chapter, section, subsection, subsubsection][number=no]

%\setupdescriptions[width=10mm]

\definedescription
  [description]
  [headstyle=bold, style=normal,
   location=hanging, width=18mm, distance=14mm, margin=0cm]

\setupitemize[autointro, packed]    % prevent orphan list intro
\setupitemize[indentnext=no]

\setupfloat[figure][default={here,nonumber}]
\setupfloat[table][default={here,nonumber}]

\setuptables[textwidth=max, HL=none]

\setupthinrules[width=15em] % width of horizontal rules

\setupdelimitedtext
  [blockquote]
  [before={\setupalign[middle]},
   indentnext=no,
  ]


\starttext

\section[scott-allen-funkhouser]{Scott Allen Funkhouser}

\thinrule

\startblockquote
Updated January 2017
\stopblockquote

\thinrule

\subsection[education]{Education}

\startdescription{2013-2019}
  {\bf PhD, Genetics and Quantitative Biology}; Michigan State
  University
\stopdescription

\startdescription{2007-2011}
  {\bf BSc, Biochemistry}; University of Washington
\stopdescription

\startdescription{2005-2007}
  {\bf Valedictorian}; Graham-Kapowsin HS
\stopdescription

\subsection[research-positions]{Research Positions}

\startdescription{2014 - Present}
  {\bf Graduate Research Assistant}; Mentor: Catherine Ernst PhD;
  Michigan State University

  {\em Investigating the role of A-to-I RNA editing in mammalian genomes
  and developing methods for the genomic prediction of complex
  phenotypes.}
\stopdescription

\startdescription{2012 - 2013}
  {\bf Research Scientist I}; Mentor: Mary Philip MD PhD; University of
  Washington

  {\em Investigated the role of a heme exporter, FLVCR, in the
  development of T lymphocytes.}
\stopdescription

\startdescription{2010 - 2011}
  {\bf Undergraduate Research Assistant}; Mentor: Chris Hague PhD;
  University of Washington

  {\em Studied novel binding partners to pertinent G-Protein coupled
  receptors.}
\stopdescription

\subsection[awards-grants-scholarships]{Awards, Grants, Scholarships}

{\bf USDA Pre-doctoral Fellowship}

{\em 2017-2019} • {\em \$95,000}

{\bf ISAG Travel Award}

{\em \$2,000 to attend the 2016 ISAG Conference in Salt Lake City, UT}

{\bf NSIF Graduate Student Travel Award}

{\em \$500 to attend 2016 NSIF meeting in Raleigh, NC}

{\bf Fred and Lucille Stamper Academic College Scholarship}

{\em 2007 - 2011} • {\em \$16,256}

\subsection[memberships]{Memberships}

{\bf ASAS PhD Student Member}

{\em 2015 -- Present}

{\bf Genetics Student Organization Officer}

\startitemize[packed]
\item
  2016-Present: {\em President}
\item
  2014-2015: {\em Second-year Representative}
\item
  2015-2016: {\em Third-year Representative and Social Chair}
\stopitemize

\subsection[selected-graduate-coursework]{Selected Graduate Coursework}

\startitemize[packed]
\item
  Molecular Biology (BMB 801)
\item
  Eukaryotic Molecular Genetics (MMG 835)
\item
  R Programming for Quantitative Genetics (ANS 824)
\item
  Advanced Statistics for Biologists (STT 814)
\item
  Intro to Statistical Genetics (STT 855)
\item
  Bayesian Inference using MCMC (FW 849)
\stopitemize

\subsection[skills]{Skills}

\startdescription{{\bf Programming}}
  Listed in order from most skilled to least skilled

  \startitemize[packed]
  \item
    The R language
  \item
    C++
  \item
    Bash
  \item
    Fortran
  \item
    Python
  \item
    Java
  \stopitemize

  Familiar with others for web development including:

  \startitemize[packed]
  \item
    Markdown
  \item
    HTML
  \item
    CSS
  \item
    Javascript
  \stopitemize
\stopdescription

\startdescription{{\bf Bioinformatics}}
  Experience using various tools, including:

  \startitemize[packed]
  \item
    Bowtie
  \item
    Tophat
  \item
    Picard
  \item
    SAMTools
  \item
    bcftools
  \item
    Variant Effect Predictor
  \item
    UCSC Genome Browser
  \stopitemize
\stopdescription

\startdescription{{\bf Software development}}
  \startitemize[packed]
  \item
    Git
  \item
    Github
  \item
    R Studio
  \item
    GNU Make
  \stopitemize

  R development packages:

  \startitemize[packed]
  \item
    devtools
  \item
    roxygen
  \item
    testthat
  \stopitemize
\stopdescription

\startdescription{{\bf Literate programming}}
  \startitemize[packed]
  \item
    knitr
  \item
    Rmarkdown
  \item
    Shiny
  \stopitemize
\stopdescription

\startdescription{{\bf Molecular Biology}}
  \startitemize[packed]
  \item
    Flow cytometry
  \item
    immunostaining
  \item
    qPCR
  \item
    PCR
  \item
    molecular cloning and techniques therein
  \item
    cell culture
  \stopitemize
\stopdescription

\subsection[publications]{Publications}

\startitemize[n,packed][stopper=.]
\item
  {\bf Funkhouser SA}, Bates RO, Ernst CW, Newcom D, Steibel JP.
  Estimation of genome-wide and locus-specific breed composition in
  pigs. TAS. 2017; doi: 10.2527/tas2016.0003
\item
  Zhao D, Hamilton JP, Hardigan M, Yin D, He T, Vaillancourt B, Reynoso
  M, {\bf Funkhouser SA} et al. Analysis of ribosome-associated mRNAs in
  rice reveals the importance of transcript size and GC content in
  translation. G3 (Bethesda). 2016;7: 203--219.
  doi:10.1534/g3.116.036020
\item
  Philip M, {\bf Funkhouser SA}, Chiu EY, Phelps SR, Delrow JJ, Cox J,
  et al. Heme Exporter FLVCR Is Required for T Cell Development and
  Peripheral Survival. J Immunol. 2015; doi:10.4049/jimmunol.1402172
\stopitemize

\subsection[pending-publications]{Pending Publications}

\startitemize[n,packed][stopper=.]
\item
  {\bf Funkhouser SA}, Steibel JP, Bates RO, Raney NE, Schenk D, Ernst
  CW. Evidence for Transcriptome-wide RNA Editing Among Sus scrofa PRE-1
  SINE Elements. bioRxiv. 2017; Available:
  \useURL[url1][http://biorxiv.org/content/early/2017/01/05/096321.abstract][][here]\from[url1]
\item
  Reeb PD, {\bf Funkhouser SA}, Ernst CW, Steibel JP. Assessing genotype
  call accuracy from RNA sequencing data.
\stopitemize

\subsection[conference-presentations-and-posters]{Conference
Presentations and Posters}

\startitemize[packed]
\item
  {\bf Funkhosuer SA}, Bates RO, CW Ernst, Newcom D, Steibel JP. (2016)
  Estimation of the composition of four U.S. swine breeds using genomic
  data. ePoster presented at the 2016 ASDA/AAS Joint Annual Meeting.
\item
  {\bf Funkhouser SA}, Steibel JP, Bates RO, Raney NE, Ernst CW. (2016)
  RNA editing in swine is associated with PRE-1 retrotransposons.
  ePoster presented at the 2016 International Society for Animal
  Genetics Conference.
\item
  {\bf Funkhouser SA}, Steibel JP, Bates RO, Raney NE, Ernst CW. (2015)
  Evidence of RNA editing in pig longissimus dorsi muscle. Oral
  presentation given at the American Dairy Science / American Society of
  Animal Science Midwest Conference. 
\stopitemize

\thinrule

\startblockquote
\useURL[url1][mailto:sfunkhouser@gmail.com][][sfunkhouser@gmail.com]\from[url1]
• (253)-720-2797 • 474 S. Shaw Lane, Room 1205 - East Lansing, Michigan,
USA
\stopblockquote

\stoptext
